\documentstyle[Flow]{article}
%
% This is an OCR copy of an English manual sent by Mrs. M.Geest together
% with her letter to Iwakuma (bear@hashi1.civil.tohoku.ac.jp) and
% has been processed by "plain2" on PC98 with a lot of manual corrections.
%                                                3/17/1992
% PAGE FORMAT for A4-size : default
\setlength{\topmargin}{0cm}
\setlength{\headsep}{20pt}
\setlength{\textheight}{24cm}
\setlength{\textwidth}{16cm}
\setlength{\oddsidemargin}{2.25cm}
\setlength{\evensidemargin}{2.25cm}
% "namelist" environment from "Raku Raku LaTeX"
% usage: \begin{namelist}{width}
\newcommand{\namelistlabel}[1]{\mbox{#1}\hfill}   % itemize
\newenvironment{namelist}[1]{%
\begin{list}{}
  {\let\makelabel\namelistlabel
   \settowidth{\labelwidth}{#1}
   \setlength{\leftmargin}{1.1\labelwidth}} }{%
\end{list}}
\begin{document}

\begin{namelist}{{\large\it Date}}

\item[{\large\it Name}]\mbox{}\\
    {\bf FLOW} --- Typeset Flow diagrams in \LaTeX\ (Version~:~2)

\item[{\large\it Date}]\mbox{}\\
     July 2, 1990

\item[{\large\it Synopsis}]\mbox{}
\begin{verbatim}
\STRUCT{struct name}{structure purpose}{statements}
\end{verbatim} For a description of the statements see section
Macros

\item[{\large\it Description}]\mbox{}\\
The {\tt Flow} macros
enable the user to create flow diagrams in a \LaTeX\  document.
The macros can be used in any type of document, within all the
standard \LaTeX\  environments.

A flow diagram in this context is
described in macros resembling a pseudo code. The diagram itself
is defined as a structure and is build from statements. Macros
are available for all standard programming statements (if, while,
action etc.).

The Language Sensitive Editor for \LaTeX, LSA, is extended to
support the creation of flow diagrams with the {\tt Flow}
macros.

The macros needed to create a flow diagram in your \LaTeX\  document
will be made available to you when you include the option {\tt Flow}
in the \verb+\documentstyle+ command at the start of
your \LaTeX\  file, as in the following example:
\begin{verbatim}
     \docrnentstyle[llpt ,Flow]{article}
\end{verbatim}
A flow diagram in the context of the {\tt Flow}
macros is called a structure. The drawing of the diagram is based
on units. A unit can be seen as the box in which an action is
described.  The unit has an attribute, the width. It determines
the width of the boxes to be drawn. Users can change the width of
units through a macro which must be used before the actual
structure is described.

By default the text in the diagrams is
typeset in the same size as the text in the document. This will
be too large. Before starting a structure it is advised to set the
desired text size. For the default setting of the unit width
\verb+\scriptsize+ is recommended.

When you run into errors like {\tt overfull vbox[]} you may have
to use a smaller text size like \verb+\tiny+.
In a default sized box 4 lines of {\tt scriptsize} text can be
placed. When {\tt tiny} is used 5 lines will fit.

Do not forget to
reset the text size to \verb+normalsize+ after the structure.

\item[{\large\it Macros}]\mbox{}\\
The available macros fall into three categories:
\begin{enumerate}
\item Width setting of the units. It must appear before the structure.
\item Definition of the structure itself.
\item Statements. They must appear within the structure
definition.
\end{enumerate}

Width setting macro is:
\begin{itemize}
\item \verb+\unitwidth=size+\\ Specifies
the minimum width of a unit. Size must be given as a standard
\LaTeX\  length.
\end{itemize}

Structure definition macro is:
\begin{itemize}
\item \verb+\STRUCT{struct-name}{struct-description}{statements}%+\\
Specifies the complete diagram. The structure name will appear at
the top of the flow diagram and the description, which can be a
short description of its purpose, will be put beside the actual
diagram. The statements of the structure, described below, must
be specified as part of the \verb+\STRUCT+ command.
\end{itemize}

Statement macros are:
\begin{itemize}
\item \verb+\ACTION{action}%+\\
Specifies a normal statement.
\item \verb+\PROC{proc-name}{proc-description}%+\\
Specifies a
special kind of action, a procedure call. The proc-name will be
put below the proc-description text in the same box, separated
by a horizontal line.
\item \verb+\LABEL{lab-name}%+\\
Specifies a label with a
label-name of only a few letters.
\item \verb+\IF{condition}\THEN{statements}\ELSE{statements}\ENDIF%+\\
Specifies an if statement
with a condition and a collection of statements in the {\tt THEN} and
the {\tt ELSE} part.
Neither the {\tt THEN} nor the {\tt ELSE} part is optional. If
one of them is not needed an empty statement, "{}", must be used.
\item \verb+\REPEAT{statements}\UNTIL{test}%+\\
Specifies a loop statement
with a collection of statements and an end condition.
\item \verb+\WHILE{condition}{statements}\ENDWHILE%+\\
Specifies a loop statement
with a start-condition and a collection of statements.
\item \verb+\CASE{case-item}{when-statements}\ENDCASE%+\\
Specifies a case statement
with a case-item and a collection of when-statements.
\item \verb+\WHEN{condition}{statements}%+\\
Part of a case statement.
Specifies a condition and a collection of statements.
\end{itemize}

Options are:
\begin{itemize}
\item \verb+\setiftext{downward}{right-hand}%+\\
Specifies the text to be put on the downward and
right-hand sides of the condition of an if statement. By default
the settings are empty. The scope for these settings depends on
the position of the command within the document.
\begin{itemize}
\item If the command occurs before a \verb+\STRUCT+
 statement, the settings remain valid for all \verb+\IF+ statements
 in all following structures until they are reset by a
 \verb+\setiftext+ command with the same scope.
 (Remember to put the \verb+\setiftext+ command after any font
 size changing commands).
\item If the command occurs inside a \verb+\STRUCT+ statement but
 outside any other commands, the settings will remain valid
 for all \verb+\IF+ statements in the same structure until
 they are reset by a \verb+\setiftext+ command with the same scope.
\item If the command occurs inside a command within a structure,
 the settings will remain valid for all \verb+\IF+ statements within
 the command (for instance an if statement within the then or else
 part of another if statement) until they are reset by
 a \verb+\setiftoxt+ command with the same scope.
\end{itemize}
It is allowed to `nest' the \verb+\setiftext+ commands, thus changing
the settings for a particular part of a structure or a
document.
\end{itemize}
Note that each line within the structure, including the
command itself, must be concluded by a \%.

The text appearing
(between the braces) in the structure definition and in all
statements is free but must adhere to the standard \LaTeX\ 
syntax. Every text is considered a paragraph in the \LaTeX\ 
context.

\item[{\large\it Files}]\mbox{}\\
     The file {\tt TEX\$INPUTS:FLOW.STY} specifies the flow macros.

\item[{\large\it See also}]\mbox{}\\
The pages on \LaTeX, LSA and NASSI in this section of the
manual.

\item[{\large\it Bugs}]\mbox{}\\
The {\tt Flow} option is mutually exclusive with the {\tt Nassi} option
because the same macro names are used.

Always put the same number
of actions in each branch ({\tt WHEN} statement) of a {\tt CASE}
statement. Only {\tt ACTION} and {\tt PROC} statements are
allowed here.

{\tt Flow} has a limit
to the number of statement macro's in one structure definition.
For example a maximum of 26 {\tt IF} macro's can be used. If one of
these limits is reached, \LaTeX\  shows some curious error
messages, like ``You cannot use = as a prefix'', which have no
relation at all to the real problem.

\item[{\large\it Example}]\mbox{}\\
The following is
an example of a structure with all possible statements. The
resulting diagram is shown below.
\begin{verbatim}
\scriptsize
\STRUCT{struct name}{structure purpose}{%
  \ACTION{initial statement}%
  \PROC{proc name}{procedure purpose}%
  \IF{condition\\ to test}%
    \THEN{%
      \ACTION{true action 1}%
      \ACTION{true action 2}%
    }%
    \ELSE{%
      \ACTION{false action}%
  }%
  \ENDIF%
  \LABEL{A}%
  \REPEAT{%
    \ACTION{statement to repeat}%
  }%
  \UNTIL{end condition}%
  \WHILE{start condition}{%
    \ACTION{statement to do}%
  }%
  \ENDWHILE%
  \CASE{case item}{%
    \WHEN{condition 1}{%
      \ACTION{statement to do}%
    }%
    \WHEN{condition 2}{%
      \ACTION{statement to do}%
    }%
    \WHEN{condition 3}{%
      \ACTION{statement to do}%
    }%
  }%
  \ENDCASE%
}%
\normalsize
\end{verbatim}
\end{namelist}
\pagebreak
\scriptsize
\STRUCT{struct name}{structure purpose}{%
  \ACTION{initial statement}%
  \PROC{proc name}{procedure purpose}%
  \IF{condition\\ to test}%
    \THEN{%
      \ACTION{true action 1}%
      \ACTION{true action 2}%
    }%
    \ELSE{%
      \ACTION{false action}%
  }%
  \ENDIF%
  \LABEL{A}%
  \REPEAT{%
    \ACTION{statement to repeat}%
  }%
  \UNTIL{end condition}%
  \WHILE{start condition}{%
    \ACTION{statement to do}%
  }%
  \ENDWHILE%
  \CASE{case item}{%
    \WHEN{condition 1}{%
      \ACTION{statement to do}%
    }%
    \WHEN{condition 2}{%
      \ACTION{statement to do}%
    }%
    \WHEN{condition 3}{%
      \ACTION{statement to do}%
    }%
  }%
  \ENDCASE%
}%
\normalsize
\end{document}
